### 2024-09-24 sections/awards.tex
Update awards.tex

@@

\begin{cvhonors}
\cvhonor
{Early Career Scholar Award}
{Best early career work and travel support for the BigSurv23 Conference, about {\pounds} 525.}
{Quito, ECU}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ECPR Joint Sessions of Workshops Grant}
{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about {\pounds} 1 350.}
{Toulouse, FRA}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about {\pounds} 1 400.}
{Bath, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} 
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about {\pounds} 2 255.} 
{Oxford, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about {\pounds} 160 000.}
{Oxford, GBR}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about {\pounds} 1 150.}
{Santiago, CHL}
{2012}
\end{cvhonors}

>>>>

%% Zurich 2024

@@

\begin{cvhonors}
\cvhonor
{Early Career Scholar Award}
{Best early career work and travel support for the BigSurv23 Conference, about USD\$700.} %% {\pounds} 525
{Quito, ECU}
{2023}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ECPR Joint Sessions of Workshops Grant}
{Travel support for the European Consortium for Political Research (ECPR) Joint Sessions of Workshops, about USD\$1 800.} %% {\pounds} 1 350
{Toulouse, FRA}
{2023}
\end{cvhonors}

@@

%% Kassel

%% Zurich 2022

%% IPSA Seminar in Madrid

\begin{cvhonors}
\cvhonor
{SLAS Postgraduate and Postdoctoral Research Award and Conference Grant} 
{Research support grant for my DPhil (PhD) project and travel support for the Society for Latin American Studies (SLAS) Annual Conference, about USD\$1 850.} %% {\pounds} 1 400
{Bath, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Travel and Book Grants} %% Re-check
{Research support grant for my DPhil (PhD) project and allowances for participation in conferences and purchase of books, about USD\$3 000.}  %% {\pounds} 2 255
{Oxford, GBR}
{2022}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{Becas Chile Doctoral Scholarship Abroad} 
{Tuition fees, transport and living expenses for pursuing a DPhil (PhD) at the University of Oxford (ANID/PFCHA/72200340), about USD\$215 000.} %% {\pounds} 160 000
{Oxford, GBR}
{2019}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{FONDECYT Thesis Writing Grant}
{Financial support for MA fieldwork (Prof. Gonzalo Delamaza, Supervisor, ANID/FONDECYT/1100877), about USD\$1 500.} %% {\pounds} 1 150
{Santiago, CHL}
{2012}
\end{cvhonors}
